```{r loading libraries - EDA expression, message=FALSE, eval=TRUE, include=TRUE}
# import::from(.from = SummarizedExperiment, colData)
# import::from(.from = DT, datatable)
# import::from(.from = ggplot2, .all=TRUE)
# import::from(.from = DataExplorer, plot_bar)
# import::from(.from = tableone, CreateTableOne)
# import::from(.from = dplyr, group_by, count)

#import::from(.from = SummarizedExperiment, colData, assay)
import::from(.from = variancePartition, fitExtractVarPartModel, sortCols, plotVarPart)
import::from(.from = doParallel, registerDoParallel)
import::from(.from = parallel, makeCluster, stopCluster)

# import utils scripts
import::from(.from = here::here("utils/rnaSelectTopVarGenes.R"), "rnaSelectTopVarGenes", .character_only=TRUE)
import::from(.from = here::here("utils/edaFunctions.R"), "varPartitionEstimate", "generatePCA", "pcaExtractVariance", "pcaPlotVariance", "pcaCorrPCs", "pcaCorrPCsPlot", .character_only=TRUE)

```


```{r EDA expression - loading objects, message=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
experiment_name="nk_tum_immunoedit_complete"
output_dir <- paste0(results_dir, "/",experiment_name,"/") # "/home/rstudio/workspace/results_dir/nk_tum_immunoedit_complete/" 
# results_dir defined in the nk_immunoediting.Rmd file

eda_plots_dir <- paste0(output_dir, "eda_plots/")
dir.create(eda_plots_dir)

# raw and filtered dds
precomputed_objects_filename <-paste0(experiment_name, "_dds_objects.RData") # "nk_tum_immunoedit_complete_dds_objects.RData" 
precomputed_objects_file <- file.path(output_dir, precomputed_objects_filename)

# log2 and vsd transformed
precomputed_transf_objects_filename <- paste0(experiment_name, "_log2_vsd_filt_objects.RData") #"nk_tum_immunoedit_complete_log2_vsd_filt_objects.RData"
precomputed_transf_objects_file <- file.path(output_dir, precomputed_transf_objects_filename)

# check if object loaded if not load
if(!exists(precomputed_objects_file)){
  load(precomputed_objects_file)
  load(precomputed_transf_objects_file)
} 

metadata <- tibble::as_tibble(SummarizedExperiment::colData(dds_filt))

key_metadata <- metadata %>%
  dplyr::select(experiment, condition_tp,condition, timepoint_cell_harvesting, day_cell_harvesting, cell_line_label, technical_replicate) 

# saving metadata
#openxlsx::write.xlsx(metadata, file = file.path(output_dir, paste0(experiment_name, "_metadata.xlsx")))

# preparing vsd per experiment ----
experiments <- unique(as.character(vsd_filt$experiment))
vsd_filt_perExp <- purrr::map(.x = experiments, .f = function(experiment_name){
  vsd_filt[,vsd_filt$experiment == experiment_name]
}) %>% setNames(experiments)
#lapply(vsd_filt_perExp, dim)
```

```{r EDA expression - define parameters, message=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
cond_interest <- "condition_tp"   # column of interest for PCA plots etc.
cond_interest_varPart <- c("condition_tp", "condition", "timepoint_cell_harvesting", "cell_line_label", "technical_replicate", "experiment")
cond_interest_varPart_corr <- c("condition_tp", "cell_line_label", "experiment", "technical_replicate")
  
# #~  (1|technical_replicate) + (1|experiment) + (1|cell_line_label) + (1|condition_tp) 
fitform_partVariance <- ~(1 | technical_replicate) + (1 | experiment) + (1 | cell_line_label) + (1 | timepoint_cell_harvesting) + (1 | condition) 
padj_cutoff = 0.05
log2FC_cutoff = 0.58 #(FC=1.5); log2FC=1.0 # (FC=2)
var_expl_needed <- 0.6         # at least 60% variance explained needed
transf_object <- vsd_filt # which object to use for pca, variance partition etc. in case there is e.g. log2norm, rlog,...

```

### Variance partition

```{r EDA expression - variance partition, message=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
# calculating overall variance partition ----
variance_partition_all <- varPartitionEstimate(transf_object = transf_object, 
                                              fitform_partVariance = fitform_partVariance,
                                              ntop_genes=1000,
                                              ncores = 12)

# calculating variance partition per experiment ----
fitform_partVariance_perExperiment <- ~(1 | technical_replicate) + (1 | cell_line_label) + (1 | timepoint_cell_harvesting) + (1 | condition)
variance_partition_perExperiment <- purrr::map(.x=names(vsd_filt_perExp), .f=function(experiment_name){
  varPartitionEstimate(transf_object = vsd_filt_perExp[[experiment_name]], 
                                              fitform_partVariance = fitform_partVariance_perExperiment,
                                              ntop_genes=1000,
                                              ncores = 12)
}) %>% setNames(names(vsd_filt_perExp))

```

```{r Variance partition plot - all, message=FALSE, eval=TRUE, include=TRUE, fig.dim = c(10, 10)}
#print(key_variables_tableOne$CatTable)
variance_partition_all_plot <- variance_partition_all$varPart_plot_annot + ggtitle("Variance partition all experiments")

print(variance_partition_all_plot)

ggsave(filename = paste0(eda_plots_dir, "variance_partition_all_plot.png"), 
       plot=variance_partition_all_plot,
       width = 20, height = 20, units = "cm")

```

Variance explained by different variables of interest. There seems to be a lot of variation coming from different experiments and cell lines. This will need to be accounted in the design or downstream batch effect removal.

```{r Variance partition table - all, message=FALSE, eval=TRUE, include=TRUE}
#print(key_variables_tableOne$CatTable)
variance_partition_all$varPart_stats %>%
  kableExtra::kbl(caption="Variance partition table - all experiments") %>%
  kableExtra::kable_material(c("striped", "hover"))
```

*Please note color coding varies between variance_partition_perExperiment
```{r Variance partition plot - per experiment, message=FALSE, eval=TRUE, include=TRUE}
variance_partition_perExperiment_plots <- purrr::map(.x=names(variance_partition_perExperiment), .f = function(experiment_name){
  variance_partition_perExperiment[[experiment_name]]$varPart_plot_annot + ggtitle(paste0("Variance partition experiment - ", experiment_name))
}) %>% setNames(names(variance_partition_perExperiment))

variance_partition_perExperiment_plots <- purrr::map(.x=names(variance_partition_perExperiment), .f = function(experiment_name){
  print(variance_partition_perExperiment_plots[[experiment_name]])
  ggsave(filename = paste0(eda_plots_dir, paste0("variance_partition_", experiment_name,"_plot.png")), 
       plot=variance_partition_perExperiment_plots[[experiment_name]],
       width = 20, height = 20, units = "cm")
}) %>% setNames(names(variance_partition_perExperiment))

```

### Principal Component Analysis (PCA)

```{r EDA expression - PCA generation, message=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
# calculating how many components are needed ----
transf_object_counts_ntop <- rnaSelectTopVarGenes(SummarizedExperiment::assay(transf_object), ntop = 1000, type = "var")
pca_object <- stats::prcomp(t(transf_object_counts_ntop), center = TRUE)
pca_results <- pcaExtractVariance(pca_object)
pca_scree_cumVarExpl <- pcaPlotVariance(pca_results, var_expl_needed = var_expl_needed)
min_components_needed <- which(pca_results$cummulative_variance > var_expl_needed)[1] # min components to get var_expl_needed 

# calculating components correlation with variables ----
#TODO:
# fix - correlation between PCs and variables of interest! - fix sample naming!
# PC_corr <- pcaCorrPCs(pca_object, metadata[cond_interest_varPart_corr], pcs = 1:min_components_needed, pval_exact = TRUE) 
# PC_corr_plot <- pcaCorrPCsPlot(PC_corr)

# calculating overall PCA ----
condition_tp_colors <- RColorBrewer::brewer.pal(length(unique(metadata$condition_tp)),"Dark2")
names(condition_tp_colors) <- levels(metadata$condition_tp)
    
pca_all <- generatePCA(transf_object = transf_object, 
                       cond_interest_varPart = cond_interest_varPart, 
                       color_variable = "condition_tp", 
                       shape_variable = "experiment",
                       ntop_genes = 1000) +
      ggtitle("Overall PCA") +
      ggplot2::scale_color_manual(values = condition_tp_colors)   
 
pca_perExperiment_plots <- purrr::map(.x=names(vsd_filt_perExp), .f = function(experiment_name){
    pca_plot <- generatePCA(transf_object = vsd_filt_perExp[[experiment_name]], 
                cond_interest_varPart = cond_interest_varPart, 
                color_variable = "condition_tp", 
                shape_variable = "cell_line_label",
                ntop_genes = 1000)
  
    pca_plot + ggtitle(experiment_name) +
      # make universal color, shape across the whole report!
      ggplot2::scale_shape_manual(values = c("A" = 16, "B" = 15, "C"=17, "D"=3)) +
      ggplot2::scale_color_manual(values = condition_tp_colors)   
}) %>% setNames(names(vsd_filt_perExp))

combined_pca_plot <- ggpubr::ggarrange(pca_perExperiment_plots$EXP9.4, 
                                       pca_perExperiment_plots$EXP9.5,
                                       pca_perExperiment_plots$EXP9.6,
                                       pca_perExperiment_plots$EXP9.7,
                                       pca_perExperiment_plots$EXP9.8, 
                                       nrow=3, ncol=2,
                                       common.legend = FALSE) #patchwork::wrap_plots(pca_perExperiment_plots, ncol=2)
```

```{r EDA expression - PCA all scree plot, message=FALSE, eval=TRUE, include=TRUE, fig.dim = c(10, 10)}

print(pca_scree_cumVarExpl)
ggsave(filename = paste0(eda_plots_dir, "pca_scree_cumVarExpl_plot.png"), 
       plot=pca_scree_cumVarExpl,
       width = 20, height = 20, units = "cm")
```

Overall PCA plot:
```{r EDA expression - PCA all plot, message=FALSE, eval=TRUE, include=TRUE, fig.dim = c(10, 10)}

print(pca_all)
ggsave(filename = paste0(eda_plots_dir, "pca_all_plot.png"), 
       plot=pca_all,
       width = 20, height = 20, units = "cm")
```

PCA plot per experiment:

```{r EDA expression - PCA per experiment plot, message=FALSE, eval=TRUE, include=TRUE, fig.dim = c(14, 14)}

print(combined_pca_plot)
ggsave(filename = paste0(eda_plots_dir, "pca_perExperiment_plot.png"), 
       plot=combined_pca_plot,
       width = 20, height = 20, units = "cm")
```
